Clustering Beat-Chroma Patterns\\ in a Large Music Database

### 2010-03-24 Paper/Paper.tex

@@

\begin{table}
\begin{center}
\begin{tabular}{|l|l|c|}
\hline
\# codes & distortion \\ \hline \hline
1 & $0.066081$ \\
10 & $0.045579$ \\
50 & $0.038302$ \\
100 & $0.035904$ \\
500 & $0.030841$ \\ \hline
\end{tabular}
\end{center}
\caption{\small{Varying codebook size using $50,000$ training samples.
    We train on patterns corresponding to $1$ bar resized to $4$ beats.
  }}
\label{tab:cbsize}
\end{table}

@@

We train a codebook of size $100$ on bars resized to $4$ beats. Then,
we take the longest sequence of bars of $4$ beats in the test set.  As
we mentioned before, $4$ beats is the most common bar size using the
Echo Nest segmentation. We then encode this sequence using an offset
of $0$, $1$, $2$ or $3$ beats. The best offset in terms of distortion
should correspond to the bar alignment relative to the original
feature matrix.

FIXME: Actually I'm (ronw) not sure how this was done.  Every 4 beat
segment was treated separately?  Its not looking for a per-song alignment?
%The good answer is an offset of $0$.

@@

\begin{table}
\begin{center}
\begin{tabular}{c|c}
%\hline
offset & \% of times chosen \\ \hline
0 & $\mathbf{62.6}$\\
1 & $16.5$\\
2 & $09.4$\\
3 & $11.5$\\
\end{tabular}
\end{center}
\caption{\small{
Best offset according to our codebook. The real one is $0$.
Random guess gives an accuracy of $25$\%.
}}
\label{tab:offset}
\end{table}

>>>>

\usepackage{booktabs}

@@

\begin{table}
\begin{center}
\begin{tabular}{llc}
\toprule
Codebook size & Distortion \\
\midrule
1 & $0.066081$ \\
10 & $0.045579$ \\
50 & $0.038302$ \\
100 & $0.035904$ \\
500 & $0.030841$ \\
\bottomrule
\end{tabular}
\end{center}
\caption{\small{Varying codebook size using $50,000$ training samples.
    We train on patterns corresponding to $1$ bar resized to $4$ beats.
  }}
\label{tab:cbsize}
\end{table}

@@

We train a codebook of size $100$ on bars resized to $4$ beats. Then,
we take the longest sequence of bars of $4$ beats in the test set.  As
we mentioned before, $4$ beats is the most common bar size using the
Echo Nest segmentation. We then encode this sequence using an offset
of $0$, $1$, $2$ or $3$ beats. The best offset in terms of distortion
should correspond to the bar alignment in the original
feature matrix.  The correct answer is an offset of $0$.

FIXME: Actually I'm (ronw) not sure how this was done.  Every 4 beat
segment was treated separately?  Its not looking for a per-song alignment?

@@

\begin{table}
\begin{center}
\begin{tabular}{cc}
\toprule
Offset & \% of times chosen \\
\midrule
0 & $\mathbf{62.6}$\\
1 & $16.5$\\
2 & $09.4$\\
3 & $11.5$\\
\bottomrule
\end{tabular}
\end{center}
\caption{\small{
Song segmentation experiment:
best offset according to our codebook. The real one is $0$.
Random guess gives an accuracy of $25$\%.
}}
\label{tab:offset}
\end{table}
